---
title: "Copper River Sockeye Test Fishery"
subtitle: "Sockeye Salmon Stock Composition Summary"
output:
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
geometry: margin=0.5in
date: "`r paste('Reported on:', format(Sys.Date(), format = '%B %d, %Y'), 'at', format(Sys.time(), format = '%I:%M %p'))`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

library(tidyverse)
library(knitr)
library(kableExtra)
library(ggpubr)
load("V:/Analysis/2_Central/Sockeye/PWSCopper/Copper Inseason 2018/copper_2018_SW26.RData")

n_geno <- get(paste0("sillys_strata_2018_SW", sw, "_n"))[sillys_strata, "Genotyped"]
n_final <- get(paste0("sillys_strata_2018_SW", sw, "_n"))[sillys_strata, "Final"]
```

# `r strata_date_range`

The following describes genetic stock composition estimates for sockeye salmon from the Copper River test fishery for `r strata_date_range`. A total of `r n_samp` fish were sampled and `r n_geno` were analyzed (`r n_final` had adequate data to include in this analysis).

```{r estimates_table, fig.align="center"}
copper_2018_dates.sum %>%
  filter(year == 2018, stat_week == sw) %>%
  select(reporting_group, mean, `5%`, `95%`) %>%
  mutate(mean = mean * 100) %>%
  mutate(`5%` = `5%` * 100) %>%
  mutate(`95%` = `95%` * 100) %>%
  kable(digits = 1, format = "latex", booktabs = TRUE, escape = FALSE, linesep = "",
        col.names = c(linebreak(x = "Reporting\nGroup", align = "l"),
                      linebreak(x = c("Stock Composition\nEstimate (\\%)", "Lower 90\\%\nCI (\\%)", "Upper 90\\%\nCI (\\%)"), align = "r"))) %>% 
  kable_styling(position = "center")
```

```{r stock_comp_figure, fig.height=6, fig.width=5, fig.align="center"}
copper_2018_dates.sum %>% 
  filter(year == 2018, stat_week == sw) %>% 
  ggplot(aes(x = reporting_group, y = mean * 100, fill = reporting_group, ymin = `5%` * 100, ymax = `95%` * 100)) +
  geom_col(colour = "black") +
  scale_fill_manual(values = PWSCopper8Groups_pub) +
  geom_errorbar(width = 0.5) +
  scale_y_continuous(breaks = seq(0, 100, 20), limits = c(0, 100), expand = c(0, 0)) +
  ylab("Stock Composition Estimates (%)") +
  xlab("Reporting Group") +
  ggtitle(paste("Genetic Stock Composition\nEstimates", strata_date_range)) +
  theme_classic(base_size = 14) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(hjust = 0.5),
        panel.grid.major.y = element_line(colour = "black", size = 0.5))
```
# 2018 Inseason Summary

Weekly summary of genetic stock composition point estimates (%). See previous releases for credibility intervals associated with each weekly estimate.

```{r weekly_summary_table}
options(knitr.kable.NA = '')
copper_2018_dates.sum %>% 
  filter(year == 2018) %>% 
  select(reporting_group, stat_week, mean) %>% 
  mutate(stat_week = factor(stat_week, levels = 26:31)) %>% 
  mutate(mean = mean * 100) %>% 
  complete(stat_week, reporting_group, fill = list(mean = NA)) %>% 
  rename(`Statistical Week` = stat_week) %>% 
  spread(reporting_group, mean) %>% 
  kable(digits = 1, format = "latex", booktabs = TRUE, escape = FALSE, linesep = "",
        col.names = c(linebreak(x = "Statistical\nWeek", align = "l"),
                      linebreak(x = c("Southwest\nPWS", "Main Bay\nNorth PWS", "Copper\nDelta", "Upper\nDelta", "Gulkana", "Tazlina\nOutlets", "Klutina", "Lower\nCopper"), align = "r"))) %>% 
  kable_styling(position = "center")
```

```{r stat_week_stock_comp_figure, fig.height=6.5, fig.width=7.5, fig.align="center"}
date_range_2018 <- c(unique(copper_2018_dates.sum$date_range), vector(mode = "character", length = 6))

copper_2018_dates.sum %>% 
  filter(year == 2018) %>% 
  select(reporting_group, stat_week, date_range, mean) %>% 
  mutate(stat_week = factor(stat_week, levels = 26:31)) %>% 
  mutate(mean = mean * 100) %>% 
  complete(stat_week, reporting_group, fill = list(mean = 0, date_range = '')) %>% 
  # mutate(date_range = factor(x = date_range, levels = unique(date_range))) %>% 
  ggplot(aes(x = stat_week, y = mean, fill = reporting_group)) +
  geom_col(position = "stack", colour = "black") +
  scale_fill_manual(values = colors8) +
  scale_y_continuous(breaks = seq(0, 100, 20), limits = c(0, 100.1), expand = c(0, 0)) +
  scale_x_discrete(labels = date_range_2018) +
  ggtitle("Comparison of Weekly Stock\nComposition Estimates") +
  ylab("Stock Composition Estimates (%)") +
  xlab("Date") +
  theme_classic(base_size = 18) +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")
```